**Title:** Lake Photic Zone Temperature across the Conterminous United States

### 2020-11-05 manuscript/manuscript.Rmd
Added nla map, pred vs obs plot, and error map

![`r fig_num("LakePhoticZonev2")`](../figures/LakePhoticZonev2.jpg)

@@

In addition to a measure of overall model performance, we used percent increase of mean-squared error to assess variable importance.  The percent increase in mean-squared error is a comparison between the true values of a variable and randomly permuted values of a specific variable on overall model performance.

@@

The final model built with the eight selected variables has a root mean-squared error of `r round(sqrt(mean(RFAll$mse)), 2)`  and adjusted R^2^ of `r round(mean(RFAll$rsq), 2)`. The model performs well across a wide range of temperatures (`r fig_num("obs_v_pred", caption = "Predicted versus measured photic zone temperature", display = "cite")`); however, at the higher and lower temperature (i.e. less than 15 °C and greater than 32 °C) the model does not perform as well but lakes with growing season temperatures at these extremes were rare and represented only `r round(extreme$perc, 2)` of lakes sampled in the 2007 and 2012 NLA.

@@

>>>>

![`r fig_num("LakePhoticZonev2")`](../figures/nla_map.jpg)

@@

We evaluated the resultant model in several ways.  First, we assess the overall model performance with traditional measures such as root mean square error of the out-of-bag residuals.  Second, we examine error by comparing the predicted versus observed temperature for all lakes.  In addition to these measures of overall model performance, we used percent increase of mean-squared error to assess variable importance.  The percent increase in mean-squared error is a comparison between the true values of a variable and randomly permuted values of a specific variable on overall model performance.

@@

The final model built with the eight selected variables has a root mean-squared error of `r round(sqrt(mean(RFAll$mse)), 2)`  and adjusted R^2^ of `r round(mean(RFAll$rsq), 2)`. The model performs well across a wide range of temperatures (`r fig_num("obs_v_pred", caption = "Predicted versus measured photic zone temperature", display = "cite")`); however, at the higher and lower temperature (i.e. less than 15 °C and greater than 32 °C) the model does not perform as well but lakes with growing season temperatures at these extremes were rare and represented only `r round(extreme$perc, 2)` of lakes sampled in the 2007 and 2012 NLA.  Additionally, there is not an obvious spatial clustering of lakes with higher error (`r fig_num("obs_v_pred_map", caption = "Map of predicted minus observed temperature for 2007 and 2012 National Lakes Assessment lakes", display = "cite")`).

@@

![`r fig_num("obs_v_pred_map")`](../figures/error_map.jpg)
